---
title: "Elderly Paper - data analysis"
author: W. Francuzik
date: 21.08.2018
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# Loading the data

```{r set_knitr_chunk_options,echo=FALSE,message=FALSE,warning=FALSE}
#bibliography: references.bib

require(knitr)
require(kfigr)
require(magrittr)
opts_chunk$set(echo=FALSE,message=FALSE,warning=F,cache = F)#,eval.after='fig.height') # important for making sure the output will be well formatted.
options(scipen=9999)

#### Citations
require(bibtex)
require(knitcitations)
#biblio <- read.bib("bib.bibtex")
cite_options(citation_format = "compatibility", style = "text",
             hyperlink = FALSE, cite.style = "numeric", super = FALSE,
             max.names = 4, longnamesfirst = FALSE, check.entries = FALSE)

require(pander)
#replace.print.methods <- function(PKG_name = "pander") {
#   PKG_methods <- as.character(methods(PKG_name))
#   print_methods <- gsub(PKG_name, "print", PKG_methods)
#   for(i in seq_along(PKG_methods)) {
#      f <- eval(parse(text=paste(PKG_name,":::", PKG_methods[i], sep = ""))) # the new function to use for print
#      assign(print_methods[i], f, ".GlobalEnv")
#   }
#}
#replace.print.methods()
## The following might work with some tweaks:
## print <- function (x, ...) UseMethod("pander")

panderOptions('table.split.table',Inf)

# Here I read data into R using the function below and save it in a native R format. 
# data <- read.spss("/home/wojtek/Documents/anaphylaxis registry/anaphylaxis/anaphylaxis_registry_02_mar_2015_mergedSD.sav",use.value.labels = TRUE,to.data.frame = T,trim.factor.names = T,trim_values = T) #this loads the databbase from spss file - watch out for errors.

# new database!!!!
# data <- read.spss("/home/wojtek/Documents/anaphylaxis registry/anaphylaxis/anaphylaxis_registry_18_apr_2016_mergedSD.sav",use.value.labels = TRUE,to.data.frame = T,trim.factor.names = T,trim_values = T) #this loads the databbase from spss file - watch out for errors.

# new database 2017 !!!!
# library("foreign")
# data3 <- read.spss("/home/wolass/Documents/anaphylaxis/anaphylaxis_registry_20_mar_2017_mergedSD.sav",use.value.labels = TRUE,to.data.frame = T,trim.factor.names = T,trim_values = T) #this loads the databbase from spss file - watch out for errors.

# save(data3,file = "data3.R") # dor database from 2015 choose data.R
load("../anaphylaxis/data3.R")
# load("data2.R")
data <- data3[,-16]
#load("data4.R")
#data <- data4
# I could make a nice table showing  mistakes in our database. 
# length(which(data$q_111=="no"&data$q_111_angioedema=="unknown"))

### Here I will introduce functions for database conformity
# for(i in c(16:55,65,75,178:205,209:220,222:223)){
  # levels(data[,i]) <- c(levels(data[,i])[1:2],NA)  
# }
# for(i in c(79:83)){
#   levels(data[,i]) <- c(levels(data[,i])[1:2],"no")  
# }
# levels(data$q_421_exercise) <- c("no","mild","moderate","vigorous",NA)

no.of.centers <- length(levels(data$b_centres_id))
no.of.countries <- length(summary(data$d_centres_country)) - length(which(summary(data$d_centres_country)==0))

no.of.cases <- length(data$b_case_id)
no.of.patients <- no.of.cases - (length(which(summary(data$b_patient_code)==2)) + length(which(summary(data$b_patient_code)==3)) +length(which(summary(data$b_patient_code)==4)) + length(which(summary(data$b_patient_code)==5)))

no.of.F <- summary(data$b_sex)[1]
no.of.M <- summary(data$b_sex)[2]

#Check this using the following line
#summary(as.factor(summary(data$b_patient_code)))


##OUTCOMES
data$rmr <- data$d_severity_rm
levels(data$rmr)<-c("I+II","I+II","III+IV","III+IV")
data$rmr2 <- data$d_severity_rm
levels(data$rmr2)<-c("I+II+III","I+II+III","I+II+III","IV")

```

Registered cases `r nrow(data)`

```{r}
data.country <- data[data$d_centres_country %in% 
                       c("Germany", "Austria", "Switzerland", "Greece", "Poland", "Spain", "France", "Bulgaria", "Italy", "Ireland"),]
```

Cases after getting rid of some low-reporting countries `r nrow(data.country)`

```{r}
d.rm <- data.country[which(data.country$d_severity_rm=="grade II"|
                             data.country$d_severity=="grade III"|
                             data.country$d_severity=="grade IV"),]
```

Cases with severity of `>= II` `r nrow(d.rm)`

```{r}
d.ch <- d.rm[which(d.rm$d_age<18),]
d.ad<- d.rm[which(d.rm$d_age>=18),]
d.ad.1 <- d.rm[which(d.rm$d_age>=18&d.rm$d_age<=40),]
d.ad.2 <- d.rm[which(d.rm$d_age>=41&d.rm$d_age<=64),]
d.ad.3 <- d.rm[which(d.rm$d_age>=65),]

```


Children `r nrow(d.ch)`, adults `r nrow(d.ad)`, 

Adults 18-40 = `r nrow(d.ad.1)`
Adults 41-64 = `r nrow(d.ad.2)`
Elderly >=65 = `r nrow(d.ad.3)`

```{r}
f.age <-function(x){ if(x>17&x<=40){
  return("young")
} else if(x>40&x<=64){
  return("middle")
} else if(x>=65){
  return("elderly")
} else {
  return(NA)
}
}
# here we change the d.rm to be oly of adults
d.rm <- d.ad

d.rm$ages <-sapply(d.rm$d_age,f.age) 

table(d.rm$b_sex,d.rm$ages)
require(rmngb)
pairwise.chisq.test(d.rm$b_sex,d.rm$ages)
```

# Atopic dermatitis
```{r}
d_410_atopic <- rep("non-atopic",nrow(d.rm))
d_410_atopic[d.rm$q_410_ad_cur=="yes"|
  d.rm$q_410_asthma_cur=="yes" |
  d.rm$q_410_rhinitis_cur=="yes"] <- "atopic"

d.rm$d_410_atopic <- d_410_atopic
table(d.rm$d_410_atopic,d.rm$ages)
pairwise.chisq.test(d.rm$d_410_atopic,d.rm$ages,p.adj = "bonf")

```

# Cardiovascular disease 

```{r}
temp <- table(d.rm$q_410_cardio_cur,d.rm$ages) 

pairwise.chisq.test(x = d.rm$q_410_cardio_cur[d.rm$q_410_cardio_cur%in%c("no","yes")] %>% {as.character(.)},
                    g = d.rm$ages[d.rm$q_410_cardio_cur%in%c("no","yes")])

```

# Urticaria

```{r}
table(d.rm$q_410_urtic_cur,d.rm$ages)

valF <- function(val){
  pairwise.chisq.test(x = val[which(val%in%c("no","yes"))] %>% as.character(),
                    g = d.rm$ages[which(val%in%c("no","yes"))])

}
valF(d.rm$q_410_urtic_cur)
```


# Mastocytosis

```{r}
table(d.rm$q_410_masto_cur,d.rm$ages)
valF(d.rm$q_410_masto_cur)
```

# Thyroid disease 

```{r}
table(d.rm$q_410_thyroid_cur,d.rm$ages)
valF(d.rm$q_410_thyroid_cur)
```

# Physical exercise 

```{r}
table(d.rm$q_421_exercise,d.rm$ages)
pairwise.chisq.test(d.rm$q_421_exercise,d.rm$ages)
```

# Psychological stress

```{r}
table(d.rm$q_422_stress,d.rm$ages)
pairwise.chisq.test(d.rm$q_422_stress,d.rm$ages)
```

# Alcohol

```{r}
table(d.rm$q_425_alcohol,d.rm$ages)
valF(d.rm$q_425_alcohol)
```

# Menstruation

```{r}
table(d.rm$q_424_menstruation,d.rm$ages)
valF(d.rm$q_424_menstruation)
```

This variable should not be taken into account I think. The elderly group does not have any menstrruation...


# infection

```{r}
table(d.rm$q_410_infect_cur,d.rm$ages)
valF(d.rm$q_410_infect_cur)
```

# repeated reaction

```{r}
table(d.rm$q_160_ever_react,d.rm$ages) 
valF(d.rm$q_160_ever_react)
```

# Elicitors

## Total

```{r}
Fun <- function(x,selector=rep(TRUE,nrow(d.rm))){
  a <- table(d.rm[selector,x],d.rm$ages[selector]) 
  b <- pairwise.chisq.test(d.rm[selector,x] %>% as.character,
                           d.rm$ages[selector] %>% as.character)
  return(list(c(x),a,b))
}

Fun("q_310_trigger",selector=rep(TRUE,nrow(d.rm)))


```

## Elicitor known 
```{r}
d.rm$elicitor_known<- rep("no",nrow(d.rm))
d.rm$elicitor_known[d.rm$q_310_trigger=="yes"] <- "yes"

Fun("elicitor_known")
```

## Elicitor suspected
```{r}
d.rm$elicitor_suspected<- rep("no",nrow(d.rm))
d.rm$elicitor_suspected[d.rm$q_310_trigger=="reasonable suspicion"] <- "yes"

Fun("elicitor_suspected")
```

## Drugs 
```{r}

d.rm$elicitor_drug<- rep("no",nrow(d.rm))
d.rm$elicitor_drug[d.rm$d_elicitor_group=="drug"] <- "yes"

Fun("elicitor_drug")
```

### analgesics
```{r}

d.rm$elicitor_analg<- rep("no",nrow(d.rm))
d.rm$elicitor_analg[!is.na(d.rm$q_332_analgesic)] <- "yes"
d.rm$elicitor_analg[d.rm$q_332_analgesic=="no"] <- "no"

Fun("elicitor_analg")
```

### antibiotics
```{r}

d.rm$elicitor_anty<- rep("no",nrow(d.rm))
d.rm$elicitor_anty[!is.na(d.rm$q_331_antibiotics)] <- "yes"
d.rm$elicitor_anty[d.rm$q_331_antibiotics=="no"] <- "no"

Fun("elicitor_anty")
```


### Local anesthetics
```{r}
d.rm$elicitor_LA<- rep("no",nrow(d.rm))
d.rm$elicitor_LA[!is.na(d.rm$q_3361_local_anaesthetics_v4)] <- "yes"
d.rm$elicitor_LA[d.rm$q_3361_local_anaesthetics_v4=="no"] <- "no"

Fun("elicitor_LA")
```


### x-ray (contrast agent)

```{r}
d.rm$elicitor_contrast<- rep("no",nrow(d.rm))
d.rm$elicitor_contrast[!is.na(d.rm$q_335_xray_cm)] <- "yes"
d.rm$elicitor_contrast[d.rm$q_335_xray_cm=="no"] <- "no"

Fun("elicitor_contrast")
```

### PPI
```{r}
d.rm$elicitor_ppi<- rep("no",nrow(d.rm))
d.rm$elicitor_ppi[!is.na(d.rm$q_339_ppi_v5)] <- "yes"
d.rm$elicitor_ppi[d.rm$q_339_ppi_v5=="no"] <- "no"

Fun("elicitor_ppi")
```

### Cardiovascular drugs

Here Only 1 patient in the youg adults group was positive for the cardio drugs. 


```{r}
d.rm$elicitor_cvd<- rep("no",nrow(d.rm))
d.rm$elicitor_cvd[which(d.rm$q_333_cardio_drugs=="ACE-inhibitor"|
                  d.rm$q_333_cardio_drugs=="Ca2+-antagonist"|
                    d.rm$q_333_cardio_drugs=="cardio drugs")] <- "yes"
# d.rm$elicitor_cvd[d.rm$q_423_at2=="yes"] <- "yes"
# d.rm$elicitor_cvd[d.rm$q_423_beta=="yes"] <- "yes"
# d.rm$elicitor_cvd[!is.na(d.rm$q_333_cardio_drugs)] <- "yes"
# d.rm$elicitor_cvd[d.rm$q_333_cardio_drugs=="no"] <- "no"


Fun("elicitor_cvd")
# pairwise.fisher.test(d.rm$elicitor_cvd,d.rm$ages)
```

## Insects
```{r}
d.rm$elicitor_insects<- rep("no",nrow(d.rm))
d.rm$elicitor_insects[!is.na(d.rm$q_340_insects)] <- "yes"
d.rm$elicitor_insects[d.rm$q_340_insects=="no"] <- "no"

Fun("elicitor_insects")
```

### Yellow jacket
```{r}
d.rm$elicitor_yj<- rep("no",nrow(d.rm))
d.rm$elicitor_yj[d.rm$q_340_insects=="yellow jacket"] <- "yes"

Fun("elicitor_yj")
```

### Bee
```{r}
d.rm$elicitor_bee<- rep("no",nrow(d.rm))
d.rm$elicitor_bee[d.rm$q_340_insects=="bee"] <- "yes"

Fun("elicitor_bee")
```

### Hornet
```{r}
d.rm$elicitor_hornet<- rep("no",nrow(d.rm))
d.rm$elicitor_hornet[d.rm$q_340_insects=="hornet"] <- "yes"

Fun("elicitor_hornet")
```

## Food

```{r}
d.rm$elicitor_food<- rep("no",nrow(d.rm))
d.rm$elicitor_food[d.rm$d_elicitor_group=="food"] <- "yes"
Fun("elicitor_food")

d.rm.f <- d.rm[d.rm$elicitor_food=="yes",]
Fun.f <- function(x,selector=rep(TRUE,nrow(d.rm.f))){
  a <- table(d.rm.f[selector,x],d.rm.f$ages[selector]) 
  b <- pairwise.chisq.test(d.rm.f[selector,x],d.rm.f$ages[selector])
  return(list(c(x),a,b))
}

```

### wheat

```{r}
d.rm.f$elicitor_wheat<- rep("no",nrow(d.rm.f))
d.rm.f$elicitor_wheat[d.rm.f$q_324_cereals=="wheat floar"] <- "yes"

Fun.f("elicitor_wheat")
```

### hazelnut

```{r}
d.rm.f$elicitor_HN<- rep("no",nrow(d.rm.f))
d.rm.f$elicitor_HN[d.rm.f$q_322_treenuts=="hazelnut"] <- "yes"

Fun.f("elicitor_HN")
```

### soy

```{r}
d.rm.f$elicitor_soy<- rep("no",nrow(d.rm.f))
d.rm.f$elicitor_soy[d.rm.f$q_326_legumes=="soy"] <- "yes"

Fun.f("elicitor_soy")
```

### celery

```{r}
d.rm.f$elicitor_celery<- rep("no",nrow(d.rm.f))
d.rm.f$elicitor_celery[d.rm.f$q_323_vegetables=="celery"] <- "yes"

Fun.f("elicitor_celery")
```

### shellfish

```{r}
d.rm.f$elicitor_shellfish<- rep("no",nrow(d.rm.f))
d.rm.f$elicitor_shellfish[d.rm.f$q_325_animal_products%in%
                          c("mussels","snails","shrimp/scampi","crab",
                            "crawfish","spiny lobster","calamari")] <- "yes"

Fun.f("elicitor_shellfish")
```

### peanut

```{r}
d.rm.f$elicitor_peanut<- rep("no",nrow(d.rm.f))
d.rm.f$elicitor_peanut[which(d.rm.f$q_326_legumes=="peanut")] <- "yes"
# d.rm$elicitor_peanut <- factor(d.rm$elicitor_peanut)

Fun.f("elicitor_peanut")
```

## Immunotherapy (SIT)

```{r}
d.rm$elicitor_SIT<- rep("no",nrow(d.rm))
d.rm$elicitor_SIT[which(d.rm$d_elicitor_group=="SIT")] <- "yes"
# d.rm$elicitor_peanut <- factor(d.rm$elicitor_peanut)

Fun("elicitor_SIT")
```



# Plots 

```{r}
require(ggplot2)
ggplot(d.rm[d.rm$d_elicitor_group!="cold",], aes(d_age,fill=d_elicitor_group))+
  geom_area(stat = 'bin',
            aes(y=..density..),
            position = "stack",
            binwidth=10,
            linetype=1,
            size =1,
            colour="black")+
  scale_fill_brewer(palette="Greys") +
  theme_classic()+
  theme(legend.position = c(1,1),legend.justification = c(1,1))+
  geom_segment(aes(xend=40,x=40,y=0,yend=0.17),linetype=2)+
  geom_segment(aes(xend=60,x=60,y=0,yend=0.17),linetype=2)


ggplot(d.rm,aes(x=d_age,y=..count..,fill=d_elicitor_group))+
  geom_density(position="fill")+
  theme_bw()+
  scale_fill_grey(guide=guide_legend(title = "Elicitor"))+
  # guides(fill=guide_legend(reverse=F))+
  ylab("Relative count")+
    geom_segment(aes(xend=40,x=40,y=0,yend=1),linetype=2)+
  geom_segment(aes(xend=60,x=60,y=0,yend=1),linetype=2)


```

So we can do it - the question now is what do we want to display? Food? or any other variables here that may be of interest?

Second plot - symptoms

## Gastrointestinal

```{r}

noyesf<- function(x){
  x[which(x!="yes")]<-"no"
  return(x)
}

d.rm$q_112_vomiting_ny <- d.rm$q_112_vomiting %>% noyesf
d.rm$q_112_abdominal_pain_ny <- d.rm$q_112_abdominal_pain %>% noyesf()
d.rm$q_112_incontinence_ny <- d.rm$q_112_incontinence %>% noyesf()
d.rm$q_112_nausea_ny <- d.rm$q_112_nausea %>% noyesf()


ggplot(d.rm[!is.na(d.rm$q_112_vomiting),],aes(x=d_age,y=..count..))+
  stat_density(position="fill",geom="line",aes(color=q_112_vomiting_ny,linetype="1"))+
  stat_density(position="fill",geom="line",aes(color=q_112_abdominal_pain_ny,linetype="4"))+
  stat_density(position="fill",geom="line",aes(color=q_112_incontinence_ny,linetype="6"))+
  stat_density(position="fill",geom="line",aes(color=q_112_nausea_ny,linetype="8"))+
  theme_bw()+
  scale_fill_grey(guide=guide_legend(title = "Elicitor"))+
  # guides(fill=guide_legend(reverse=F))+
  ylab("Relative count")+
  geom_segment(aes(xend=40,x=40,y=0,yend=0.5),linetype= 2, color = "gray")+
  ylim(c(0,0.5))+
  geom_segment(aes(xend=64,x=64,y=0,yend=0.5),linetype= 2, color="gray")+
  guides(color="none",
         linetype=guide_legend(title = "Symptom"))+
  scale_linetype_manual(values=c(1,4,3,8),
                        labels=c("vomiting",
                                   "abdominal pain",
                                   "incontinence",
                                   "nausea"))+
  theme(legend.position = c(0.1,0.99),
        legend.justification = c(0,1),
        legend.background = element_rect(fill="transparent"))
  

```

## Skin

```{r}

ggplot(d.rm[!is.na(d.rm$q_111_erythema_flush_v5),],
       aes(x=d_age,y=..count..))+
  stat_density(position="fill",geom="line",aes(color=q_111_angioedema%>% noyesf,linetype="1"))+
  stat_density(position="fill",geom="line",aes(color=q_111_urticaria%>% noyesf,linetype="4"))+
  stat_density(position="fill",geom="line",aes(color=q_111_pruritus%>% noyesf,linetype="6"))+
  stat_density(position="fill",geom="line",aes(color=q_111_erythema_flush_v5%>% noyesf,linetype="8"))+
  theme_bw()+
  scale_fill_grey(guide=guide_legend(title = "Elicitor"))+
  # guides(fill=guide_legend(reverse=F))+
  ylab("Relative count")+
  geom_segment(aes(xend=40,x=40,y=0.2,yend=0.7),linetype= 2, color = "gray")+
  ylim(c(0.2,0.7))+
  geom_segment(aes(xend=64,x=64,y=0.2,yend=0.7),linetype= 2, color="gray")+
  guides(color="none",
         linetype=guide_legend(title = "Symptom"))+
  scale_linetype_manual(values=c(1,4,3,8),
                        labels=c("angiooedema",
                                   "urticaria",
                                   "pruritus",
                                   "erythema"))+
  theme(legend.position = c(0.7,0.5),
        legend.justification = c(0,0),
        legend.background = element_rect(fill="transparent"))
  

```

## Respiratory 

```{r}

ggplot(d.rm[!is.na(d.rm$q_113_wheezing_expiratory_distress_v5),],aes(x=d_age,y=..count..))+
  stat_density(position="fill",geom="line",aes(color=q_113_dyspnea %>% noyesf,linetype="1"))+
  stat_density(position="fill",geom="line",aes(color=q_113_wheezing_expiratory_distress_v5%>% noyesf,linetype="2"))+
  stat_density(position="fill",geom="line",aes(color=q_113_chest_tightness_v5%>% noyesf,linetype="3"))+
  stat_density(position="fill",geom="line",aes(color=q_113_respiratory_arrest%>% noyesf,linetype="4"))+
  theme_bw()+
  scale_fill_grey(guide=guide_legend(title = "Elicitor"))+
  # guides(fill=guide_legend(reverse=F))+
  ylab("Relative count")+
    geom_segment(aes(xend=40,x=40,y=0,yend=0.7),linetype=2, color = "gray")+
  ylim(c(0.00,0.7))+
  geom_segment(aes(xend=64,x=64,y=0,yend=0.7),linetype=2,color = "gray")+
  guides(color="none",
         linetype=guide_legend(title = "Symptom"))+
  scale_linetype_manual(values=c(1,4,3,8),
                        labels=c("dyspnea",
                                 "Expiratory distress",
                                 "Chest tightness",
                                 "respiratory arrest"))+
  theme(legend.position = c(0.01,0.3),
        legend.justification = c(0,0),
        legend.background = element_rect(fill="transparent"))
```

## Cardiac

```{r}
ggplot(d.rm[!is.na(d.rm$q_114_loss_of_consciousness),],
       aes(x=d_age,y=..count..))+
  stat_density(position="fill",geom="line",aes(color=q_114_dizziness %>% noyesf,linetype="1"))+
  stat_density(position="fill",geom="line",aes(color=q_114_loss_of_consciousness%>% noyesf,linetype="2"))+
  stat_density(position="fill",geom="line",aes(color=q_114_cardiac_arrest%>% noyesf,linetype="3"))+
  stat_density(position="fill",geom="line",aes(color=q_114_tachycardia%>% noyesf,linetype="4"))+
  theme_bw()+
  scale_fill_grey(guide=guide_legend(title = "Elicitor"))+
  # guides(fill=guide_legend(reverse=F))+
  ylab("Relative count")+
    geom_segment(aes(xend=40,x=40,y=0,yend=0.7),linetype=2, color = "gray")+
  ylim(c(0,0.7))+
  geom_segment(aes(xend=64,x=64,y=0,yend=0.7),linetype=2,color= "gray")+
  guides(color="none",
         linetype=guide_legend(title = "Symptom"))+
  scale_linetype_manual(values=c(1,4,3,8),
                        labels=c("Dizziness",
                                 "Loss of consciousness",
                                 "Cardiac arrest",
                                 "Tachychardia"))+
  theme(legend.position = c(0.1,0.95),
        legend.justification = c(0,1),
        legend.background = element_rect(fill="transparent"))
```

# Risk of developing a biphasic reaction

## with concomitant hypotension

left Biphasic, top - Hypotension as a symptom. Alle cases, no age differentiation:

```{r}
table(d.rm$q_130_biphasic_v4,d.rm$q_114_hypotension_collapse_v5) %>% 
  {summary(.[2:3,1:2])}
```


## with unknown trigger as an elicitor 

Unknown elicitor showed relevant meanig that unknown trigger-cases were more often connected with biphasic reactions 


```{r}
table(d.rm$q_130_biphasic_v4,d.rm$q_310_trigger) %>% {.[2:3,1:2]}
t <- table(d.rm$q_130_biphasic_v4,d.rm$q_310_trigger) %>% {.[2:3,1:2]} %>% prop.table(2)
dimnames(t) <- list(Biphasic = c("not biphasic","biphasic"),
                    Trigger = c("unknown","known"))
t
table(d.rm$q_130_biphasic_v4,d.rm$q_310_trigger) %>% {.[2:3,1:2]} %>% summary()

```

```{r}
e_423_five <- rep("no",length(d.rm[,1]))
e_423_five[which(d.rm$q_423_ace=="yes"|
                 d.rm$q_423_asa=="yes"|
                 d.rm$q_423_at2 == "yes"|
                 d.rm$q_423_beta == "yes"|
                 d.rm$q_423_ppi_v6 == "yes")] <- "yes"
d.rm$e_423_five <- factor(e_423_five)

e_420_CoF_incl_infect <- rep("no",length(d.rm[,1]))
e_420_CoF_incl_infect[which(
  d.rm$q_4212_exercise_intensity=="vigorous eg. running, heavy manual work, competitive sport"|
  d.rm$q_4241_menstruation=="yes"|
  d.rm$q_425_alcohol=="yes"|
  d.rm$q_422_stress == "yes"|
  d.rm$e_423_five=="yes"|
  d.rm$q_410_infect_cur == "yes"
    )] <- "yes"

d.rm$e_420_CoF_incl_infect <- factor(e_420_CoF_incl_infect)
```

## Biphasic reaction depending on the trigger group 

```{r}
t <- table(d.rm$d_elicitor_gr5,d.rm$q_130_biphasic_v4)
t
t %>% {.[,2:3]} %>% 
  pairwise.chisq.test()

chisq.test(t[c(1,5),2:3])
```

# e_420_CoF_incl_infect

```{r}
table(d.rm$e_420_CoF_incl_infect,d.rm$ages)
valF(d.rm$e_420_CoF_incl_infect)
```

# e_423_five

```{r}
table(d.rm$e_423_five,d.rm$ages)
valF(d.rm$e_423_five)
```


# Differences between Age groups and time to reaction

```{r}
t <- table(d.rm$ages,d.rm$q_120_time_between_v4)[,3:8]
t
pairwise.chisq.test(t)
```